Experiences with Planning for Natural Language Generation

### 2009-06-03 trunk/Papers/ci-spark/discussion.tex
some details

We can draw both positive and negative conclusions from our experiments about
the state of planning for modern NLG applications. On the one hand, we found
that modern planners are very good at dealing with the \emph{search} problems
that arise in the NLG-based planning problems we investigated; the search
time reported by most planners was often a very small fraction of the total
running time of the planner. In the sentence generation domain, FF's Enforced
Hill-Climbing strategy finds plans corresponding to 25-word sentences in
about a second. It is hard to compare this number to a baseline because there
are no shared benchmark problems, but FF's search outperforms a greedy search
algorithm, and the performance is competitive with other sentence generators,
which similarly employ special-purpose algorithms. Thus research on search
strategies for planning has paid off; in particular, the Enforced
Hill-Climbing heuristic outperforms the best-first strategy to which FF 2.3
switches for some problem instances. Similarly, SGPLAN's performance on the
GIVE domain is very convincing and fast enough for this application.

@@

We are also aware that the time a planner invests in preprocessing can pay
off during search, and that such techniques have been invaluable in improving
the overall running time of modern planners. However, we still suggest that
the inability of current planners to scale to larger domains limits their
usefulness for applications beyond NLG as well. Furthermore, we feel that the
problem of preprocessing receives less research attention than it deserves:
if the problem is scientifically trivial then we challenge the planning
community to develop more efficient implementations that only ground
operators by need; otherwise, we look forward to future publications on this
topic. To support this effort, we offer our planning domains as benchmarks
for future research and competitions.\footnote{The PDDL problem generators
for our NLG domains are available at \texttt{http://\todo{TODO}}.}

Finally, we found it very convenient that the recent International Planning
Competitions provide a useful entry point for selecting and obtaining current
planners. Nevertheless, our experiments exposed several bugs in the planners
we tested, which required us to change their source code to make them scale
to our inputs. We also found that different planners that solve the same
class of planning problems (e.g., STRIPS, ADL, etc.) sometimes differ in the
variants of PDDL that they support. These differences range from fragments of
ADL that can be parsed to sensitivity, to the order of declarations and the
use of ``objects'' rather than ``individuals'' as the keyword for declaring
the universe. We propose that the case for planning as a mature technology
with professional-quality implementations could be made more strongly if such
discrepancies were harmonized.

>>>>

We can draw both positive and negative conclusions from our
experiments about the state of planning for modern NLG
applications. On the one hand, we found that modern planners are very
good at dealing with the \emph{search} problems that arise in the
NLG-based planning problems we investigated.
% I don't think we want to talk about this yet - AK
%; the search time reported
%by most planners was often a very small fraction of the total running
%time of the planner. 
In the sentence generation domain, FF's Enforced
Hill-Climbing strategy finds plans corresponding to 25-word sentences
in about a second. It is hard to compare this number to a baseline
because there are no shared benchmark problems, but FF's search
performance is similar to that of a greedy, incomplete special-purpose
algorithm, and competitive to other sentence generators as well. Thus
research on search strategies for planning has paid off; in
particular, the Enforced Hill-Climbing heuristic outperforms the
best-first strategy to which FF 2.3 switches for some problem
instances. Similarly, SGPLAN's performance on the GIVE domain is very
convincing and fast enough for this application.

@@

We are also aware that the time a planner invests in preprocessing can pay
off during search, and that such techniques have been invaluable in improving
the overall running time of modern planners. However, we still suggest that
the inability of current planners to scale to larger domains limits their
usefulness for applications beyond NLG as well. Furthermore, we feel that the
problem of preprocessing receives less research attention than it deserves:
if the problem is scientifically trivial then we challenge the planning
community to develop more efficient implementations that only ground
operators by need; otherwise, we look forward to future publications on this
topic. To support this effort, we offer our planning domains as benchmarks
for future research and competitions.\footnote{The PDDL problem generators
for our NLG domains are available at
\url{http://www.coli.uni-saarland.de/~koller/projects/crisp}.}

Finally, we found it very convenient that the recent International Planning
Competitions provide a useful entry point for selecting and obtaining current
planners. Nevertheless, our experiments exposed several bugs in the planners
we tested, which required us to change their source code to make them scale
to our inputs. We also found that different planners that solve the same
class of planning problems (e.g., STRIPS, ADL, etc.) sometimes differ in the
variants of PDDL that they support. These differences range from fragments of
ADL that can be parsed, to sensitivity to the order of declarations and the
use of ``objects'' rather than ``individuals'' as the keyword for declaring
the universe. We propose that the case for planning as a mature technology
with professional-quality implementations could be made more strongly if such
discrepancies were harmonized.
